---
title: "Introducción a tidymodels"
author: "Víctor Macías E."
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```


class: middle

# Beneficios de tidymodels

- Estandarizar notación a través de distintos tipos de algoritmos de aprendizaje automático.

- Fácilmente se puede modificar el preprocesamiento, la elección de algoritmo y la optimización de parámetros. hyperparameter tuning


---

class: middle

Entre los paquetes incluidos en `tidymodels` se encuentran:

1) rsamples - to split the data into training and testing sets (as well as cross validation sets)
2) recipes - to prepare the data with preprocessing (assign variables and preprocessing steps)
3) parsnip - to specify and fit the data to a model
4) yardstick and tune - to evaluate model performance
5) workflows - combining recipe and parsnip objects into a workflow (this makes it easier to keep track of what you have done and it makes it easier to modify specific steps) 
6) tune and dials - model optimization (more on what hyperparameters are later too!)
Modeling Data in the Tidyverse 676
7) broom - to make the output from fitting a model easier to read


---

class: middle

# Paso 1: Dividir los datos entre training and testing dataset

```{r}
library(rsample)
set.seed(1234)

split_iris <-initial_split(iris, prop = 2/3)

training_iris <- training(split_iris)
testing_iris <- testing(split_iris)

```

